\ProjectName{}: A Database for Missing Data

### 2016-12-14 presentation/main.tex
presentation: cleaned up
presentation: added example

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=ieee]{biblatex}
\usepackage{booktabs}
\usepackage{hyperref} % load after other packages
\usepackage{todonotes}
\presetkeys{todonotes}{inline}{}

@@

\begin{frame}[fragile]{Motivating Example}
\todo{motivating example}
\end{frame}

@@

\begin{frame}[fragile]{Imputation Algorithm}
\begin{itemize}
	\item Iterative algorithm using regression trees: \textit{Chained Equations Regression Trees} (CERT)\cite{burgette2010multiple}
	\item Significant cost to perform on entire dataset
	\item \ProjectName{} allows flexible use
\end{itemize}
\scriptsize

\begin{algorithm}[H]
\scriptsize
\input{../paper/algorithms/cert.tex}
\end{algorithm}
\end{frame}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=ieee]{biblatex}
\usepackage{booktabs}
\usepackage{hyperref} % load after other packages
\usepackage{todonotes}
\presetkeys{todonotes}{inline}{}
\usepackage[style=ieee]{biblatex}

\usepackage{listings} % code samples with syntax hl
% listings settings
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{red},    % comment style
  frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
}

@@

\begin{frame}[fragile]{Motivating Example}
\begin{itemize}
	\item An analyst wants to explore relationships between polling data and survey data on household landline ownership
	\item There is an issue with non-responses in survey data
	\item They issue an ImputeDB query and get an effective response
\end{itemize}

\begin{figure}
\begin{lstlisting}[language=SQL]
SELECT polling.ST, AVG(acs.TEL)
FROM polling, acs
WHERE polling.ST = acs.ST
  AND polling.ERROR > 50         -- 5 percentage points
GROUP BY polling.ST;
\end{lstlisting}
\caption{A typical analyst query on ACS data}
\label{fig:example-query}
\end{figure}
\end{frame}

\begin{frame}[fragile]{Motivating Example: Plan}
\begin{itemize}
	\item ImputeDB adds an impute as necessary for the aggregation
	\item It does not need to impute before then as \verb|acs.ST| is not affected by non-responses and thus has no missing values
\end{itemize}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{../paper/figures/example.png}
    \caption{Query plan generated by ImputeDB prioritizing imputation quality.}
    \label{fig:query-plan}
\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Imputation Algorithm}
\begin{itemize}
	\item Iterative algorithm using regression trees: \textit{Chained Equations Regression Trees} (CE-CERT)\cite{burgette2010multiple}
	\item Significant cost to perform on entire dataset
	\item \ProjectName{} allows flexible use
\end{itemize}
\scriptsize

\begin{algorithm}[H]
\scriptsize
\input{../paper/algorithms/cart.tex}
\end{algorithm}
\end{frame}

@@

\begin{frame}[t,allowframebreaks]{References}
  \nocite{*}
  \printbibliography
 \end{frame}
